Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-25 sattose/paper.tex
Talking about clone types

\section{Redefining type-2 and type-3 clones}

>>>>

\section{Redefining type-2 and type-3 clones}
In a 2007 survey by Roy et al \cite{roy2007survey} he defined four types of clones:

\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
